### 2014-02-23 paper/concrete.tex
Start building combined version.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
More tweaks.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{figure}
    \begin{code}

    \end{code}

>>>>

\begin{figure}

\begin{mathpar}
\inferrule[I-stepT]
{|
conf tS (te) -> conf tS' te'
|}
{|
coconf iS tS (cconf id il (iniE (IT te)), ldots)
.->
iS ; tS' ; sched step (cconf id il (iniE (IT te')), ldots)
|}

\and
% This rule is not complete, needs the FV condition
\inferrule[C-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|it1 = cconf id il (iniE id')|\\
|itnew = cconf id' il (TI ie)|\\
|fresh (id')|
}
{|
coconf iS tS (lconf id il (iniE (fork ie)), ldots)
.->
iS'; tS; sched fork (it1, ldots, itnew)
|}
\end{mathpar}
